\documentclass[10pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage[a4paper,top=1.05cm,bottom=0.85cm,left=1.35cm,right=1.35cm]{geometry}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{ragged2e}

\definecolor{sectionblue}{RGB}{46,116,181}
\hypersetup{colorlinks=true,urlcolor=blue}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2.2pt}
\setlist[itemize]{
  leftmargin=4.4mm,
  labelsep=1.5mm,
  itemsep=0.5pt,
  topsep=0.7pt,
  parsep=0pt,
  partopsep=0pt
}
\newcommand{\lead}[1]{\textcolor{sectionblue}{\textbf{#1}}}

\begin{document}
\fontsize{9.75}{10.35}\selectfont
\justifying

\begin{flushright}
\textbf{\fontsize{10.5}{11}\selectfont Dr. St\'ephane Ga\"el R. Ekodeck}\\
LIRIMA, TEAM GRIMCAPE, University of Yaounde I, Cameroon\\
\href{mailto:stephane-gael.ekodeck@facsciences-uy1.cm}{stephane-gael.ekodeck@facsciences-uy1.cm}\\
June 10, 2026
\end{flushright}
\vspace{-1.5mm}

The Editor-in-Chief\\
\textit{Information Sciences}\\
Elsevier

\vspace{1mm}
Dear Editor-in-Chief,

We respectfully submit our manuscript, \textbf{``Limits of Fibonacci
Index-Gap Coding: Complete Stream Costs, Compression Bounds, and Structural
Controls,''} for consideration as a Research Article
in \textit{Information Sciences}.

\lead{Scope fit.} The journal explicitly includes information theory,
algorithm design, computer-system evaluation, and data compression. The
manuscript studies a lossless positional representation under exact stream
accounting: every model, delimiter, selector, length field, and padding bit
required for reconstruction is measured. It combines analytical bounds,
algorithm specification, compiled evaluation, and structural controls.

\lead{Principal results.}
\begin{itemize}
  \item \textbf{Exact accounting:} A serialized format and a
  necessary-and-sufficient gain inequality determine whether a complete
  positional stream is shorter than its input, without treating metadata as
  free. Here, complete cost is defined within the serialized stream boundary.
  \item \textbf{Formal and empirical validation:} The transform is proved
  bijective; its sufficient term bound is calibrated on Canterbury and
  Silesia; generic 2048-bit integers are shown analytically and empirically to
  lie far above that bound; and a compiled implementation verifies every
  decoding round trip on complete corpora and the 100\,MB enwik8 benchmark.
  \item \textbf{Structural controls:} Lucas indices, ordinary binary set-bit
  positions, zero-block bitmaps, and boundary-zero trimming separate
  number-system effects from positional sparsity and simpler zero structure.
  \item \textbf{Reproducibility:} The public package provides the format
  implementation, tests, configurations, result tables, figure-generation
  scripts, and exact seeds.
\end{itemize}

\lead{Evidence and interpretation.} A full-corpus sweep over five block sizes
places the best FISA ratios at 92.15\% for Canterbury and 98.78\% for Silesia,
but only one and two files compress, respectively. Matched zero-bitmap and
zero-trim controls are smaller, and established codecs win every paired file
comparison. The manuscript treats this outcome as a limit of the Fibonacci
construction, not as evidence for a competitive general-purpose codec.

\lead{Relevance to readers.} The framework is applicable to
information-processing methods that introduce shared dictionaries, codebooks,
model parameters, block selectors, or other amortized side information. It
offers researchers and practitioners a reproducible procedure for separating
payload reduction from complete, decodable system cost.

\lead{Author declarations.}
\begin{itemize}
  \item \textbf{Originality and exclusive submission:} The manuscript is
  original, has not been published previously, and is not under consideration
  elsewhere.
  \item \textbf{Author approval:} All named authors have approved the
  manuscript, the authorship order, and the stated contributions.
  \item \textbf{Competing interests and funding:} The authors declare no
  competing interests. This research received no external funding.
  \item \textbf{Ethical compliance:} The study involves no human participants,
  animals, personal data, or clinical interventions; it uses public benchmark
  corpora, synthetic data, and offline computational experiments.
\end{itemize}

We believe that the combination of information-theoretic analysis, exact
format accounting, compression experiments, and reproducible negative
evidence fits the theory-and-practice scope of \textit{Information Sciences}.
Thank you for considering this submission.

\begin{center}
Yours sincerely,
\end{center}
\vspace{0.5mm}

\textbf{Dr. St\'ephane Ga\"el R. Ekodeck} (Corresponding Author)\\
\textit{ORCID: 0000-0002-8094-8832}\\
LIRIMA, TEAM GRIMCAPE, University of Yaounde I, Yaounde, Cameroon\\
\href{mailto:stephane-gael.ekodeck@facsciences-uy1.cm}{stephane-gael.ekodeck@facsciences-uy1.cm}\\
\textbf{Co-authors:} Herv\'e Tal\'e Kalachi, Serge Alain Eb\'el\'e, Norbert
Djong Wang, and Chantal Marguerite Mveh-Abia.

\end{document}
